Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = support / lhs.rhsCourse.support,
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = NA
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support

>>>>

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
                             T ~ (support / lhs.rhsCourse.support)),
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = 1 #dummy variable
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support
